\section{User Stories and Functionaliy}

For the E-commerce website there are two main User-stories. There is an Admin-user and a Customer-User.
\\
\subsection{Customer Role and Functionality:}
\begin{itemize}
    \item The customer should be able to browse products and be able to add them to a shopping basket. 
        \begin{itemize}
            \item The added product should appear in the shopping basket. 
            \item The price of the product should be added to the price of the items in the shopping basket.
        \end{itemize}
    \item The customer should be able to checkout the items in the shopping basket.
        \begin{itemize}
            \item he products in the shopping basket should be handled as an order
            
            \item After checking out the basket should become empty
            
            \item The stock of each item ordered should be reduced according to its respective quantity.
            
            \item After the customer checks out a receipt should be sent to the user via email. 
        \end{itemize}
    \item The customer should be able to preform payments. 
        \begin{itemize}
            \item The money should be transferred to the company
            \item Payment information should remain secure
        \end{itemize}
    \item The customer should be able to read about relevant information about the company to increase trustworthiness. 
    \item The customer should be able to sort and view  products given relevant categories e.g. Price, Category, Stock. 
    \item The customer should be able to see quantity of products. 
    \item The customer should be presented with deals, bundles of sorts for inspiration of purchase.
    \item The customer should be able to write reviews and and leave ratings of products. 
\end{itemize}

\subsection{Admin Role and Functionality:}

\begin{itemize}
    \item The admin should be able to do everything that the user can do.
    \item The admin should be able to add products.
    \item The admin should be able to remove products. 
    \item The admin should be able to add categories. 
    \item The admin should be able to remove categories. 
    \item The admin should be able to alter the availability of the products. 
    \item The admin should be able to change information about the company.
    \item The admin should be able to change handle status on order.
\end{itemize}





•Keep a prioritized backlog: e.g. a list of identified functions that will go into current and future sprints.•Small Sprints: Make small development cycles, producing demos (e.g., every other week), each one adding a small set of functions as identified above. If time is short, drop functions and finish in time.

•Test-driven: define test cases early. They should be saved and reused over and over.

•Get ready for the sprint review with your supervisor (lab assistants). You should be able to present demo and documentation (see below) and have a plan for the next sprint.