\newpage

\section{User Stories}\label{app:user_stories}

\subsection{Visitor Role and Functionality:}

\begin{itemize}
    \item The Visitor should be able to read about relevant information
    about the company to increase trustworthiness.
    \item The Visitor should be able to sort and view  products given
    relevant categories e.g. Price, Category, Stock.
    \item The Visitor should be able to see quantity of products. 
    \item The Visitor should be presented with deals, bundles of sorts for
    inspiration of purchase.
    \item The Visitor should be able to register for an account on the site for Customer functionality.
\end{itemize}


\subsection{Customer Role and Functionality:}

\begin{itemize}
    \item The Customer should be able to browse products and be able to add
    them to a shopping basket.
    \begin{itemize}
        \item The added product should appear in the shopping basket.
        \item The price of the product should be added to the price of the
        items in the shopping basket.
    \end{itemize}
\item The Customer should be able to checkout the items in the shopping basket.
    \begin{itemize}
        \item The products in the shopping basket should be handled as an order
        \item After checking out the basket should become empty.
        \item The stock of each item ordered should be reduced according to
        its respective quantity.
        \item After the customer checks out a receipt should be sent to the
        user via email.
    \end{itemize}
\item The Customer should be able to preform payments.
    \begin{itemize}
        \item The money should be transferred to the company
        \item Payment information should remain secure, this using Https.
    \end{itemize}
    \item The Customer should be able to write reviews and leave ratings
    of products.
    \item The Customer should be able to recieve a receipt via E-mail. 
\end{itemize}

\subsection{Admin Role and Functionality:}

\begin{itemize}
    \item The admin should be able to do everything that the user can do.
    \item The admin should be able to add products.
    \item The admin should be able to remove products. 
    \item The admin should be able to add categories. 
    \item The admin should be able to remove categories. 
    \item The admin should be able to alter the availability of the products. 
    \item The admin should be able to change information about the company.
    \item The admin should be able to change handle status on order.
\end{itemize}
